On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-01-25 MS.tex
remove seedling model, no longer needed
small editing in abstract and results

\begin{document}
\mstitlepage
\noindent
\parindent=1.5em
\addtolength{\parskip}{.3em}
\doublespacing
\linenumbers
\section{Summary 327/350}\label{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item A plant's growth rate is seen as a central element of its ecological strategy, and as determined by its traits. Yet the literature is inconsistent about the empirical correlation between functional traits and growth, casting doubt on the capacity of some prominent traits to influence growth rate.

@@

\item Although we were able to confirm several of our theoretical predictions, major knowledge gaps size still exist, despite a sizeable literature on traits and growth. For example, for one-third of the trait considered, the majority ($>$ 75\%) of reported correlations with growth came from a single ontogenetic stage.

@@

Cheaper stem construction (low wood density or stem density) increases the marginal rate of leaf deployment per total mass increment ($\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$), and consequently increases growth rate in height and diameter (eqs. \ref{eq:eq2}-\ref{eq:eq4}; Table \ref{tab:trade-offs}). Disadvantages associated with cheap stem construction take the form of higher mortality and so are not reflected in growth equations. Under this scenario, wood density is negatively correlated to growth rate across all ontogenetic stages. Because the relative expenditure on stem compared to leaf increases as plants grow larger, the relationship between wood density and growth may also strengthen in larger plants. A similar shift is expected for growth in mass when expressed in relative terms. However, when expressed as absolute growth, the predicted relationship is non-significant \citep[see also][]{Enquist-1999}.

@@

We had hypotheses for seed mass and SLA, about a change in the correlation between trait and absolute growth rate was used instead of relative growth rate, or as mass was used instead of diameter and height. For seed mass, effects size differed significantly between relative growth rate and absolute growth rate at seedling stage; as expected the correlation with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI not overlapping). For SLA, the correlation was expected to shift from positive to non significant if growth in mass was measured on absolute instead of relative terms; however, here none of the data have been measured with absolute rates in the seedling stage (Fig. \ref{fig:figA8}).
For other traits, effect size were generally consistent between relative growth rate and absolute growth rate when both measurement were available. Some differences occurred but they were not easily attributed to any single cause. For instance for wood density, the correlation at juvenile stage shifted from negative with relative growth rate to non significant with absolute growth rate (i.e CI included zero, Fig. \ref{fig:fig4}b). The correlation coefficients recorded for absolute growth rate came from \citet{Augspurger:1984ct} and unlike others they used wood density values from adult plants together with growth from juveniles.

@@

Overall our study met quality criteria expected for meta-analysis in ecology (Table \ref{tab:meta}). The impact of publication bias was seemingly trivial (See Appendix \ref{app:growth-equation}, Fig. \ref{fig:figA7}). The extent of heterogeneity was high, but was substantially explained by our core hypothesis of an effect of ontogenetic stage for SLA and seed mass (Appendix \ref{app:supp_info_analyses}). There was no indication of a temporal change in the effect size being reported within stages (Appendix \ref{app:supp_info_analyses}, Fig. \ref{fig:figA9}). Finally, our results were unlikely to be biased by dominance of one or a few studies that measured a large number of responses, since when multiple responses were condensed into a single average within a trait and within a study, outcomes were very similar (Fig. \ref{fig:figA5}).

>>>>

\begin{document}
\mstitlepage
\noindent
\parindent=1.5em
\addtolength{\parskip}{.3em}
\doublespacing
\linenumbers
\section{Summary 307/350}\label{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item A plant's growth rate is seen as a central element of its ecological strategy, and as determined by its traits. Yet the literature is inconsistent about the empirical correlation between functional traits and growth, casting doubt on the capacity of some prominent traits to influence growth rate.

@@

\item Although we were able to confirm several of our theoretical predictions, major knowledge gaps still exist in the trait literature. For example, for one-third of the trait considered, the majority ($>$ 75\%) of reported correlations with growth came from a single ontogenetic stage.

@@

Cheaper stem construction (low wood density or stem density) increases the marginal rate of leaf deployment per total mass increment ($\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$), and consequently increases growth rate in height and diameter (eqs. \ref{eq:eq2}-\ref{eq:eq4}; Table \ref{tab:trade-offs}). Disadvantages associated with cheap stem construction take the form of higher mortality and so are not reflected in growth equations. Under this scenario, wood density is negatively correlated to growth rate across all ontogenetic stages. Because the relative expenditure on stem compared to leaf increases as plants grow larger, the relationship between wood density and growth may also strengthen in larger plants. A similar shift is expected for growth in mass when expressed in relative terms. However, when expressed as absolute growth, the predicted relationship is non-significant along all plant size\citep[see also][]{Enquist-1999}.

@@

We had hypotheses for seed mass, SLA and wood density, about a change in the correlation between trait and absolute growth rate was used instead of relative growth rate, or as mass was used instead of diameter and height. For seed mass, effects size differed significantly between relative growth rate and absolute growth rate at seedling stage; as expected the correlation with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI not overlapping). For SLA, the correlation was expected to shift from positive to non significant if growth in mass was measured on absolute instead of relative terms; however, here none of the data have been measured with absolute rates in the seedling stage (Fig. \ref{fig:figA8}). For wood density, some differences occurred but they were not easily attributed to any single cause. In particular, the correlation at juvenile stage shifted from negative with relative growth rate to non significant with absolute growth rate (i.e CI included zero, Fig. \ref{fig:fig4}b). Yet, the correlation coefficients recorded for absolute growth rate came from \citet{Augspurger:1984ct}, and unlike others they used wood density values from adult plants together with growth from juveniles. So it was not possible to distangle the effect of growth measurement from the effect of trait origine. For other traits, effect size were generally consistent between relative growth rate and absolute growth rate when both measurement were available.

@@

Overall our study met quality criteria expected for meta-analysis in ecology (Table \ref{tab:meta}). The impact of publication bias was seemingly trivial (See Appendix \ref{app:heterogeneity}, Fig. \ref{fig:figA7}). The extent of heterogeneity was high, but was substantially explained by our core hypothesis of an effect of ontogenetic stage for SLA and seed mass (Appendix \ref{app:supp_info_analyses}). There was no indication of a temporal change in the effect size being reported within stages (Appendix \ref{app:supp_info_analyses}, Fig. \ref{fig:figA9}). Finally, our results were unlikely to be biased by dominance of one or a few studies that measured a large number of responses, since when multiple responses were condensed into a single average within a trait and within a study, outcomes were very similar (Fig. \ref{fig:figA5}).
